Differential Expression - MSSM-Penn-Pitt - DLPFC - Dx

### 2020-07-29 individual-cohorts/MSSM-Penn-Pitt_DLPFC_DE.Rmd
do not cache githubr

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn22043922';
activityName = 'Differential Expression';
activityDescription = 'Differential Expression - Dx';

>>>>

```{r synapse.parameters, include=FALSE, cache=FALSE}
parentId = 'syn22043922';
activityName = 'Differential Expression';
activityDescription = 'Differential Expression - Dx';
